---
title: "Graphs"
author: "Asta Kvedaraitė"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#if(!require("treemap"))install.packages("treemap")
#if(!require("d3treeR"))install.packages("d3treeR")
#if(!require("hrbrthemes"))install.packages("hrbrthemes")
```
# Dendrogram 
```{r}
sample <- read.csv("../../2darbas/output/correctedSample.csv")
beta <- readRDS("../../2darbas/output/betab.rds")
anno <- readRDS("../../Komanda/output/annotation.rds")

head(sample)
head(as.data.frame(anno))
head(as.data.frame(beta))

unique(sample$sample_plate)
chr8 <- anno[anno$chr == "chr8",]
chr8body <- chr8[chr8$UCSC_RefGene_Group == "Body",]
nrow(chr8)
as.data.frame(chr8body)
chr8bodyI <- chr8body[chr8body$Type == "I",]
as.data.frame(chr8bodyI)
plate1 <- sample[sample$sample_plate == " Plate 1",]
plate1
nrow(plate1)
data <- beta[chr8bodyI$Name, plate1$sample_id]
nrow(data)
ncol(data)
#data has chr8 and Plate_1
as.data.frame(data)
```

```{r}

hc <- hclust(dist(data))
dhc <- as.dendrogram(hc)

# set the margin
par(mar=c(4,4,2,2))

# Plot the Second group
plot(dhc[[2]] , main= "zoom on a part of the dendrogram")
specific_leaf <- dhc[[2]][[1]][[2]]
plot(specific_leaf)

plot(hc, labels = FALSE)

```
```{r}
if(!require("GGally"))install.packages("GGally")
library(GGally)
library(ggplot2)
library(hrbrthemes)
library(moduleColor)


tm <- matrix(nrow = nrow(data), ncol = 2)
tm[1:5, 1:2]
for (i in 1:nrow(data)){
    mean <- mean(as.numeric(data[i,]))
    tm[i,] <- c(rownames(data)[i], mean)
}
tm <- tm[order(tm[,2], decreasing = TRUE),]

tdata <- t(data[tm[1:100,1],])
tdata <- as.data.frame(tdata)
tdata$status <- plate1$sample
tdata
#for (i in 1:ncol(tdata)){
#  if (as.character(tdata$status[i]) == "Control") {
#    tdata$stnum[i] <- 2 
#  }else {
#    tdata$stnum[i] <- 4 
#  }
#}

#typeof(plate1$sample)
#as.character(plate1$sample)
ggparcoord(tdata,
    columns = 1:(ncol(tdata)-1), groupColumn = ncol(tdata),
    scale="uniminmax",
     showPoints = TRUE
    )
```


#So if I Want to color each leaf of the Tree, I have to change the attribute of each leaf. This can be done using the dendrapply function. So I create a function that # # add 3 attributes to the leaf : one for the color (“lab.col”) ,one for the font “lab.font” and one for the size (“lab.cex”).
i=0
colLab<<-function(n){
    if(is.leaf(n)){
       #I take the current attributes
        a=attributes(n)
        
        #I deduce the line in the original data, and so the treatment and the specie.
        ligne=match(attributes(n)$label,data[,1])
        treatment=data[ligne,3];
            if(treatment=="Low"){col_treatment="blue"};if(treatment=="High"){col_treatment="red"}
        specie=data[ligne,2];
            if(specie=="dicoccoides"){col_specie="red"};
        if(specie=="dicoccum"){col_specie="Darkgreen"};if(specie=="durum"){col_specie="blue"}
        
         #Modification of leaf attribute
        attr(n,"nodePar")<-c(a$nodePar,list(cex=1.5,lab.cex=1,pch=20,
                                            col=col_treatment,lab.col=col_specie,lab.font=1,lab.cex=1))
      }
    return(n)
}
dL <- dendrapply(dhc, colLab)
plot(dL , main="structure of the population")


if(!require("rlang"))install.packages("rlang")
library(rlang)
if(!require("ggraph"))install.packages("ggraph")

library(ggraph)
if(!require("igraph"))install.packages("igraph")
library(igraph)
library(tidyverse)
theme_set(theme_void())


ggraph(data, layout = 'dendrogram', circular = FALSE) + 
  geom_edge_diagonal() 





#RIDGELINE PLOT

# Libraries
library(tidyverse)
library(hrbrthemes)
install.packages("viridis")
library(viridis)

# Load dataset from github
data <- read.table("https://raw.githubusercontent.com/zonination/perceptions/master/probly.csv", header=TRUE, sep=",")
data <- data %>% 
  gather(key="text", value="value") %>%
  mutate(text = gsub("\\.", " ",text)) %>%
  mutate(value = round(as.numeric(value),0)) %>%
  filter(text %in% c("Almost Certainly","Very Good Chance","We Believe","Likely","About Even", "Little Chance", "Chances Are Slight", "Almost No Chance"))

install.packages("ggridges")
library(ggridges)

data %>%
  mutate(text = fct_reorder(text, value)) %>%
  ggplot( aes(y=text, x=value,  fill=text)) +
    geom_density_ridges(alpha=0.6, bandwidth=4) +
    scale_fill_viridis(discrete=TRUE) +
    scale_color_viridis(discrete=TRUE) +
    theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    ) +
    xlab("") +
    ylab("Assigned Probability (%)")





as.data.frame(beta)
head(sample)
cor <- 1-cor(beta)
head(cor)
test <- data.frame(sample$sample_plate, sample$age)

treemap::treemap(test,
                 index = c("sample.sample_plate", "sample.age"),
                 vSize = "sample.age"
            )

