---
title: "2darbas3"
author: "Asta Kvedaraite & Marius Survila"
date: "April 1, 2020"
output: html_document
---
```{r}
beta<- readRDS("../../Komanda/output/beta.rds")

pData<- readRDS("../../Komanda/output/pData.rds")

annotation<- readRDS("../../Komanda/output/annotation.rds") 

```

#12. Calculating IACs for all pairs of samples and \
examining the distribution of IACs in the dataset
```{r}

dim(beta)
#beta=beta[,1:ncol(beta)]
IAC=cor(beta,use="p")
hist(IAC,sub=paste("Mean=",
    format(mean(IAC[upper.tri(IAC)]),digits=3))) 

```
#Performing hierachical clustering (average linkage)
using 1-IAC as a distance metric
```{r}
library(cluster)
cluster1=hclust(as.dist(1-IAC),method="average")
plot(cluster1,cex=0.7,labels=dimnames(beta)[[2]],
     sub = "", xlab = "1 - IAC")


```
# Another way to visualize outliers is to calculate the
mean IAC for each array and examine this distribution
```{r}

meanIAC=colMeans(IAC)
sdCorr=sd(meanIAC)
numbersd=(meanIAC-mean(meanIAC))/sdCorr
plot(numbersd)
abline(h=-3) 

```

#Identifying outliers that are depicted in the dendrogram.\
Also removing those outliers.
```{r}
sdout=-3
outliers=dimnames(beta)[[2]][numbersd<sdout]
outliers

beta=beta[,numbersd>sdout]
dim(beta) 
beta_save <- beta
```
#Iterations that are supoosed to remove outliers and\
improve distribution of IAC and mean, remove outliers.
```{r}

for(i in c(1:2)){
  IAC=cor(beta,use="p")
  hist(IAC,sub=paste("Mean=",
      format(mean(IAC[upper.tri(IAC)]),digits=3))) 
  
  cluster1=hclust(as.dist(1-IAC),method="average")
  #plot(cluster1,cex=0.7,labels=dimnames(beta)[[2]],
  #     sub = "", xlab = "1 - IAC")
  
  meanIAC=colMeans(IAC)
  sdCorr=sd(meanIAC)
  numbersd=(meanIAC-mean(meanIAC))/sdCorr
  plot(numbersd)
  abline(h=-3) 
  
  sdout=-3
  outliers=dimnames(beta)[[2]][numbersd<sdout]
  outliers
  
  beta=beta[,numbersd>sdout]
  dim(beta) 
}

```
#Checking data after iterations\
Mean got higher and there are less outliers.\
```{r}

IAC=cor(beta,use="p")
hist(IAC,sub=paste("Mean=",
    format(mean(IAC[upper.tri(IAC)]),digits=3))) 

dim(beta)
```

```{r}
saveRDS(beta, "../../Komanda/output/betab.rds")

```
